### 2023-02-19 paper-thesis/chapters/10-coc.tex
Some layout fixes
Type checking example

There is only one sort: Expr. The syntax definition does not have a separate sort for types, as types may be arbitrary expressions in a dependently typed language. The following constructors exist:
\begin{itemize}
	\item \verb|Type| is the Type of Types.
	\item \verb|Var| is a variable, it uses the lexical sort \verb|ID|, which is defined as \verb|[a-zA-Z\_][a-zA-Z0-9\_]*|.
	\item \verb|FnType| is the type of a function. It assigns a name to its first argument to allow the return type of the function to depend on the argument type. It is right associative, meaning \verb|A -> B -> C| is interpreted as \verb|A -> (B -> C)|. 
	\item \verb|FnConstruct| creates an anonymous function (lambda function).
	\item \verb|FnDestruct| applies a function to an argument. It is left associative, meaning \verb|a b c| is interpreted as \verb|(a b) c|.
	\item \verb|Let| is a let binding. It introduces a substitutable variable.
\end{itemize}

@@

>>>>

There is only one sort: Expr. The syntax definition does not have a separate sort for types, as types may be arbitrary expressions in a dependently typed language. The following constructors exist:
\begin{itemize}
	\item \verb|Type| is the Type of Types.
	\item \verb|Var| is a variable, it uses the lexical sort \verb|ID|, which is defined as \\ \verb|[a-zA-Z\_][a-zA-Z0-9\_]*|.
	\item \verb|FnType| is the type of a function. It assigns a name to its first argument to allow the return type of the function to depend on the argument type. It is right associative, meaning \verb|A -> B -> C| is interpreted as \verb|A -> (B -> C)|. 
	\item \verb|FnConstruct| creates an anonymous function (lambda function).
	\item \verb|FnDestruct| applies a function to an argument. It is left associative, meaning \verb|a b c| is interpreted as \verb|(a b) c|.
	\item \verb|Let| is a let binding. It introduces a substitutable variable.
\end{itemize}

@@

\section{An example}
\todo{Example}

\begin{figure}[h]
	\figuresection{Type checking let}
	\begin{mathpar}
	\mprset{vskip=0.3ex}
		\inferrule{
			\inferrule{
			}{
			\toe{s_0}{\co{Type}()}{\co{Type}()}
			}
			\\ \toe{s_1}{b}{\co{Type}()}
		}{
			\toe{s_0}{\co{Let}("T", \co{Type}(), b)}{\co{Type}()}
		}
	\mprset{vskip=0ex}
	\end{mathpar}

	\figuresection{Type checking let body}
	\begin{mathpar}
		\mprset{vskip=0.7ex}
		\inferrule{
			\toe{s_1}{\co{FnConstruct}("v", \co{Type}(), \co{Var}("v"))}{\co{FnType}("v", \co{Type}(), \co{Type}())}
			\\\\ \bhr{\scope{s_1}{\co{FnType}("v", \co{Type}(), \co{Type}())}}{[]}{\scope{s_1}{\co{FnType}("v", \co{Type}(), \co{Type}())}}
			\\\\ \toe{s_1}{\co{Var}("T")}{\co{Type}()}
			\\ \beq{\co{Type}()}{\co{Type}()}
			\\ \bred{s_2}{\co{Type}()}{\co{Type}()}
		}{
			\toe{s_1}{\co{FnDestruct}(\co{FnConstruct}("v", \co{Type}(), \co{Var}("v")), \co{Var}("T")))}{\co{Type}()}
		}
		\mprset{vskip=0ex}
	\end{mathpar}

	\figuresection{Type checking function}
	\begin{mathpar}
		\mprset{vskip=0.7ex}
		\inferrule{
			\toe{s_1}{\co{Type}()}{\co{Type}()}
			\\ \beq{\co{Type}()}{\co{Type}()}
			\\\\ \bred{s_1}{\co{Type}()}{\co{Type}()}
			\\ \toe{s_3}{\co{Var}("v")}{\co{Type}()}
		}{
			\toe{s_1}{\co{FnConstruct}("v", \co{Type}(), \co{Var}("v"))}{\co{FnType}("v", \co{Type}(), \co{Type}())}
		}
		\mprset{vskip=0ex}
	\end{mathpar}

	\figuresection{Corresponding Scope Graph} \\
	\begin{tikzpicture}[scopegraph, node distance = 2.5em and 2.5em]
		\node[scope] (s0) {$s0$};

		\node[scope, right of = s0, xshift=5em] (s1) {$s1$};
		\draw (s1) edge[] (s0);
		\node[type, above of = s1] (s1l) {$\texttt{T = Type()}$};
		\draw (s1) edge[type] (s1l);

		\node[scope, right of = s1, xshift=6em] (s2) {$s2$};
		\draw (s2) edge[] (s1);
		\node[type, above of = s2] (s2l) {$\texttt{v = Type()}$};
		\draw (s2) edge[type] (s2l);

		\node[scope, below right of = s1, xshift=7em, yshift=-3em] (s3) {$s3$};
		\draw (s3) edge[] (s1);
		\node[type, above of = s3] (s3l) {$\texttt{v : Type()}$};
		\draw (s3) edge[type] (s3l);
	\end{tikzpicture}
	\caption{Type checking example}
	\label{fig:type-check-example}
\end{figure}

### 2023-02-19 paper-thesis/chapters/98-relatedwork.tex
Meeting results
Type checking example

In chapter \ref{ch:comp-haskell} and \ref{ch:comp-lambdapi} we already compared our implementation with two different implementations.

@@

The implementation in this paper requires performing substitutions in types immediately, as types don't have a scope. Van Antwerpen et al.~\cite[sect 2.5]{scopes_as_types} present an implementation of System F that does lazy substitutions, by using scopes as types. It would be interesting to see if this approach could also apply to the Calculus of Constructions, where types can be arbitrary terms.

@@

\paragraph{}

>>>>

In chapter \ref{ch:comp-haskell} and \ref{ch:comp-lambdapi} we already compared our implementation with two different implementations. In this chapter we discuss remaining related work.
TODO TODO TODO

\section{Other languages implemented in Statix}

In this thesis, we implemented a dependently typed language in Statix. In the following work, other languages are implemented in Statix:

@@

The implementation in this paper requires performing substitutions in types immediately, as types don't have a scope. Van Antwerpen et al.~\cite[sect 2.5]{scopes_as_types}~\cite{nameres} present an implementation of System F in Statix that does lazy substitutions, by using scopes as types. It would be interesting to see if this approach could also apply to the Calculus of Constructions, where types can be arbitrary terms.

\paragraph{Correct by Construction Language Implementations}

Construction Language Implementations~\cite{Rouvoet21} describes how to create a declarative specification of a language in Statix, and then to use a dependently typed language to integrate the specification of well-typing in the representation of the program that is being interpreted or transformed. The work from this thesis and ours could be combined, by using our dependently typed languages to do this verification.

\section{Other dependently typed languages}

We already implemented the calculus of constructions in Haskell (chapter~\ref{ch:comp-haskell}) and LambdaPi (chapter~\ref{ch:comp-lambdapi}), and compared the implementation in Statix with these implementations.

Below are some dependently typed languages, we discuss what make these languages unique and if these languages could be implemented in Statix:

@@

\paragraph{Other}
